Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-08 sec_summary.tex
first intro
I think it contains all we want to say and i need fine tuning on the pythia and recent work from christian tomorrow.
update on sec6

\section{Conclusions}

Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE. The measured associated yield is found to be consistent with the previous results from CMS experiment. The ridge yield, for the first time, has been observed in events including hard processes. Furthermore, it is found to be independent of the hardness of the events. This observation is important for the study of the origins of the ridge in small collision systems.

>>>>

% !TEX root = paper.tex

\section{Conclusions}
\label{sec:summary}

ALICE has measured the $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider. The spectrum of the ridge yield has been measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class. The result has been compared with CMS measurement and shown that the results are compatible. Further understandings of the correlations in small system have been tried by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$. The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) shows enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases. The results have been compared with PYTHIA8 string shoving calculation, showing comparable enhancement as data.
